---
title: "Rui Fu's CV"
author: Rui Fu
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/resume.css', 'css/styles.css', 'css/academicons.css']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- TRUE

# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/1tlN1S2XvhmSfGjk5ytwZ8T_SQrPeB5fs1wDmUuICt0k"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE


CV_PDF_LOC <- "https://github.com/raysinensis/cv/raw/master/rf_cv.pdf"
CV_HTML_LOC <- "raysinensis.com"


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')
```



```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================
<p align="center">
  <img width="111" src="https://storage.googleapis.com/nygc-wp-599886722202-wp-data/wp-media/nygc-logo-footer2.svg">
</p>

```{r}
# When in export mode the little dots are unaligned, so fix that. 
# if(PDF_EXPORT){
#   glue("View this CV online with links at _{CV_HTML_LOC}_")
# } else {
#   glue("[<i class='fas fa-download'></i> Download a PDF of this CV]({CV_PDF_LOC})")
# }
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
contact_info %>% 
  glue_data("- <i class='fa fa-{icon}'></i> {contact}") #%>% str_replace("fa fa-google", "ai ai-google-scholar")
```

Main
================================================================================

Rui Fu {#title}
--------------------------------------------------------------------------------

```{r}
print_text_block(text_blocks, 'header')
```

```{r}
print_text_block(text_blocks, 'intro')
```


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```


Research Experience {data-icon=vial data-concise=true}
--------------------------------------------------------------------------------

::: aside
```{r}
print_text_block(text_blocks, 'research_experience_aside')
```
:::

```{r}
print_section(position_data, 'research_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->
<!-- <br> -->

Publications, as First or Corresp. Author {data-icon=user-edit}
--------------------------------------------------------------------------------

::: aside
```{r}
print_text_block(text_blocks, 'academic_articles1_aside')
```
:::

```{r}
print_section(position_data, 'academic_articles1')
```

Publications, as Contributing Author {data-icon=book}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'academic_articlesCO')
```

Recognition and Funding {data-icon=award}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'other_articles')
```

Posters and Presentations {data-icon=chart-area}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'poster_articles')
```

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

::: aside
```{r}
print_text_block(text_blocks, 'teaching_experience_aside')
```
:::

```{r}
print_section_nodate(position_data, 'teaching_positions')
```

Mentoring Experience {data-icon=user-friends}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'ment_positions')
```

<!-- These breaks just force a new page so section doesnt get cut off -->
<!-- <br> -->
<!-- <br> -->

Diversity, Equity, and Inclusion {data-icon=handshake-o}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'other_div')
```

Service and Training  {data-icon=bullhorn}
--------------------------------------------------------------------------------

::: aside
```{r}
print_text_block(text_blocks, 'other_articles_aside')
```
:::

```{r}
print_section(position_data, 'other_train')
```

<!-- These breaks just force a new page so section doesnt get cut off -->
<!-- <br> -->
<!-- <br> -->

Science Outreach  {data-icon=fish}
--------------------------------------------------------------------------------

::: aside
```{r}
print_text_block(text_blocks, 'outreach_aside')
```
:::

```{r}
print_section_nodate(position_data, 'outreach')
```

```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Generated with [pagedown](https://github.com/rstudio/pagedown). 

Code at [github.com/raysinensis/cv](https://github.com/raysinensis/cv).

Last updated on `r Sys.Date()`.
